\LARGE\textbf{Designing Studies and Evaluating Research Results:\\ Type M and Type S Errors for\\ Pearson Correlation Coefficient }

### 2021-02-08 Documents/Paper_main/Paper_main.Rnw
review Giulia e Claudio

Psychological science is increasingly committed to scrutinize its published findings by promoting large-scale replication efforts \parencite{camererEvaluatingReplicabilityLaboratory2016, camererEvaluatingReplicabilitySocial2018, ebersoleManyLabsEvaluating2016, kleinInvestigatingVariationReplicability2014, kleinManyLabsInvestigating2018, opensciencecollaborationEstimatingReproducibilityPsychological2015}. In replication studies, the protocol of a previously published study is repeated as closely as possible with a new sample. Interestingly, many replication studies found smaller effects than originals, suggesting a sort of decline effect from original studies to replications \parencite{camererEvaluatingReplicabilitySocial2018, opensciencecollaborationEstimatingReproducibilityPsychological2015, schoolerTurningLensScience2014}. Among the many factors that could explain such decline, one relates to a feature of study design: statistical power \parencite{protzkoDeclineEffectsTypes2017}. In particular, it is plausible for original studies to have lower statistical power than their replications. When underpowered studies are analyzed using thresholds, such as statistical significance levels, effects passing such thresholds have to exaggerate the true effect size \parencite{buttonPowerFailureWhy2013, gelmanTypeErrorMight2017, ioannidisWhyMostDiscovered2008, ioannidisEmergenceLargeTreatment2013, laneEstimatingEffectSize1978}. Indeed, as will be extensively shown below, in underpowered studies only large effects correspond to values that can reject the null hypothesis and be statistically significant. As a consequence, if the original study was underpowered and found an exaggerated estimate of the effect, the replication results will likely show a decline. The concept of statistical power finds its natural development in the Neyman-Pearson framework of statistical inference and this is the framework that we adopt in this contribution. Contrary to the Null Hypothesis Significance Testing (NHST), the Neyman-Pearson approach requires to define both the \textit{Null Hypothesis} (i.e., usually, but not necessarily, the absence of an effect) and the \textit{Alternative Hypothesis} (i.e., the magnitude of the expected effect). Further discussion on the Neyman and Pearson approach and a comparison with the NHST is available in \textcite{altoeEnhancingStatisticalInference2020} and \textcite{gigerenzerNullRitualWhat2004}.

When conducting hypothesis testing, we are used to think about inferential risks considering only the Type I error (i.e., the probability $\alpha$ of rejecting the Null Hypothesis if this is true) and the Type II error (i.e., the probability $\beta$ of rejecting the Alternative Hypothesis if this is true). Power analysis, then, is usually conducted to define the sample size required to obtain a given level of the statistical power (i.e., the probability 1-$\beta$ to find a statistically significant result if the Alternative Hypothesis is true). All this leads to a narrow focus on statistical significance of hypothesis testing overlooking another important aspect of statistical inference: effect size estimation.

Effect size estimation and statistical significance are closely related and effect size exaggeration is a corollary consequence of low statistical power that might not be evident at first.This point can be highlighted estimating the Type M (magnitude) and Type S (sign) errors characterizing a study design \parencite{gelmanPowerCalculationsAssessing2014}. Given a study design (i.e., sample size, statistical test directionality, $\alpha$ level and plausible effect size formalization), Type M error indicates the factor by which a statistically significant effect would be, on average, exaggerated. Type S error indicates the probability to find a statistically significant effect in the opposite direction to the one considered plausible. The analysis that researchers perform to consider Type M and Type S errors in their research practice is called \emph{design analysis}, given the special focus posed into considering the design of a study \parencite{altoeEnhancingStatisticalInference2020, gelmanPowerCalculationsAssessing2014}.

It is evident that both errors are defined starting from a reasoned guess on the plausible magnitude and direction of the effect under study, which is called \emph{plausible effect size} \parencite{gelmanPowerCalculationsAssessing2014}. A plausible effect size is an assumption the researchers make about which is the expected effect value in the population. This should not be based on some noisy results from a pilot study but, rather, it should derive from an extensive evaluation of the literature (e.g., theoretical or literature reviews and meta-analyses). If all the main results in a given topic, considering a specific experiment design, indicate that the correlation range between $r = .15$ and $r =.25$, for example, we could reasonably choose as plausible effect size a value within this range. Or even better, we could consider multiple values to evaluate the results in different scenarios. Note that the definition of a plausible effect size is inevitably highly context dependent so any attempt to provide references values would not be useful but, rather, it would prevent researchers from reasoning about the phenomenon of interest. Even in case of not available information, which would question the exploratory/confirmatory nature of the study, researchers still could evaluate which effect would be considered relevant (e.g., from clinical or economic perspective) and define the plausible effect size according to that.
Why do these errors matter? The exaggeration of effect sizes, in the right or in the wrong direction, has important consequences on a theoretical and applied level. On a theoretical level, studies’ designs with high Type M and Type S errors can foster distorted expectations on the effect under study, triggering a vicious cycle for the planning of future studies. This point is relevant also for the design of replication studies, which could turn out to be underpowered if they do not take into account possible inflations of the original effect \parencite{buttonPowerFailureWhy2013}. When studies are used to inform policymaking and real-world interventions, implications can go beyond the academic research community and can impact society at large. In these settings, we could assist to a “hype and disappointment cycle” \parencite{gelmanOverconfidenceResearchCertainty2019}, where true effects turn out to be much less impressive than expected. This can produce undesirable consequences on people’s lives, a consideration that invites researchers to assume responsibility in effectively communicating the risks related to effects quantification.

Type M (magnitude) and Type S (sign) errors are not widely known in the psychological research community but their consideration during the research process has the potential to improve current research practices, for example, by increasing the awareness that design choices have on possible studies' results. In a previous work we illustrated Type M and Type S errors using Cohens’\emph{d} as a measure of effect size \parencite{altoeEnhancingStatisticalInference2020}. In this contribution we aim to to further increase familiarity with Type M and Type S errors, considering another common effect size measures in psychology: Pearson correlation coefficient, $\rho$.  The rest of this article is organized as follows: introduction to Type M and Type S errors; description of what is a design analysis and how to conduct one; analysis of Type S and Type M errors when varying alpha levels and hypothesis directionality. Moreover, the two appendices present further implications of design analysis for Pearson correlation (Appendix \ref{sec:appendix_a}) and an extensive illustration of the R functions for design analysis for Pearson correlation (Appendix \ref{sec:appendix_b}).

@@

Pearson correlation coefficient is a standardized effect size measure indicating the strength and the direction of the relationship between two continuous variables \parencite{cohenStatisticalPowerAnalysis1988, ellisEssentialGuideEffect2010}. Even though the correlation coefficient is widely known, we briefly go over its main features using an example. Imagine that we were interested to measure the relationship between anxiety and depression in a population and we plan a study with \emph{n} participants, where, for each participant, we measure the level of anxiety (i.e., variable X) and the level of depression (i.e., variable Y). At the end of the study we will have n pairs of values X and Y. The correlation coefficient helps us answer the questions: how strong is the linear relationship between anxiety and depression in this population? Is the relationship positive or negative? Correlation ranges from -1 to +1, indicating respectively two extreme scenarios of perfect negative relationship and perfect positive relationship\footnote{Correlation indicates a relationship between variables but does not imply causation. We do not discuss
this relevant aspect here but we refer the interested reader to \parencite{rohrerThinkingClearlyCorrelations2018}}. Since the correlation coefficient is a dimensionless number, it is a signal to noise ratio where the signal is given by the covariance between the two variables ($cov(x,y)$) and the noise is expressed by the product between the standard deviations of the two variables ($S_x  S_y$; see Formula\ref{eq:correlation}). Following the conventional standards, in this contribution we will use the symbol $\rho$ to indicate the correlation in the population and the symbol \emph{r} to indicate the value measured in a sample.
\begin{equation}
\label{eq:correlation}
r=\frac{cov(x,y)}{S_x S_y}.
\end{equation}

@@

Researchers can consider Type M and Type S errors in their practice by performing a \emph{design analysis} \parencite{altoeEnhancingStatisticalInference2020, gelmanPowerCalculationsAssessing2014}. Ideally, a design analysis should be performed when designing a study. In this phase it is specifically called \emph{prospective design analysis} and it can be used as a sample size planning strategy where statistical power is considered together with Type M and Type S errors. However, design analysis can also be beneficial to evaluate the inferential risks in studies that have already been conducted and where the study design is known. In these cases, Type M and Type S errors can support results interpretation by communicating the inferential risks in that research design. When design analysis happens at this later stage, it takes the name of \emph{retrospective design analysis}. Note that retrospective design analysis should not be confused with post-hoc power analysis. The former defines the plausible effect size according to previous results in the literature or other information external to the study, whereas the latter defines the plausible effect size based on the observed results in the study and it is a widely-deprecated practice \parencite{goodmanUsePredictedConfidence1994a, gelmanDonCalculatePosthoc2019a}.

In the following sections we illustrate how to perform prospective and retrospective design analysis using some examples. We developed two R functions\footnote{An R-package was subsequently developed and now is available on CRAN, PRDA: Conduct a Prospective or Retrospective Design Analysis \url{https://cran.r-project.org/web/packages/PRDA/index.html}.} to perform design analysis for Pearson correlation, which are available at the page \url{https://osf.io/9q5fr/}. The function to perform a prospective design analysis is \texttt{pro\_r()}. It requires as input the plausible effect size (\texttt{rho}), the statistical power (\texttt{power}), the directionality of the test (\texttt{alternative}) which can be set as: “\texttt{two.sided}”, “\texttt{less}” or “\texttt{greate}r” . Type I error rate (\texttt{sig\_level}) is set as default at 5\% and can be changed by the user. The \texttt{pro\_r()} function returns the necessary sample size to achieve the desired statistical power, Type M error rate, the Type S error probability, and the critical value(s) above which a statistically significant result can be found. The function to perform retrospective design analysis is \texttt{retro\_r()}. It requires as input the plausible effect size, the sample size used in the study, and the directionality of the test that was performed. Also in this case, Type I error rate is set as default at 5\% and can be changed by the user.  The function \texttt{retro\_r()} returns the Type M error rate, the Type S error probability, and the critical value(s). For further details regarding the R functions refer to Appendix~\ref{sec:appendix_b}.

@@

@@

However, in the case of $\rho \neq 0$, the sample correlation is no longer normally distributed. As we have previously seen, the sampling distribution is skewed for large values of $\rho$ and small sample sizes. Thus, the test statistic of interest does not follow a \emph{t}-distribution.\footnote{Note that the \emph{t}-distribution is defined as the distribution of a random variable T where $T = \frac{Z}{\sqrt{V/df}}$. With \emph{Z} a standard Normal, \emph{V} a Chi-squared distribution with \emph{df} the degrees of freedom. Thus, if the sample correlation is no longer approximately normally distributed the test-statistic is not longer \emph{t}-distributed.} To overcome this issue, the Fisher transformation was introduced \parencite{fisherFrequencyDistributionValues1915}:
\begin{equation}
  F(r) = \frac{1}{2}\ ln \frac{1+r}{1-r} = \text{arctanh}(r).
\end{equation}
Applying this transformation, the resulting sampling distribution is approximately Normal with $\text{mean} = F(\rho)$ and $\text{SE} = \frac{1}{\sqrt{n-3}}$. Thus, the test statistic follows a standard Normal distribution and statistical inference is performed considering the \emph{Z}-scores.

>>>>

Psychological science is increasingly committed to scrutinize its published findings by promoting large-scale replication efforts, where the protocol of a previous study is repeated as closely as possible with a new sample\parencite{camererEvaluatingReplicabilityLaboratory2016, camererEvaluatingReplicabilitySocial2018, ebersoleManyLabsEvaluating2016, kleinInvestigatingVariationReplicability2014, kleinManyLabsInvestigating2018, opensciencecollaborationEstimatingReproducibilityPsychological2015}. Interestingly, many replication studies found smaller effects than originals \parencite{camererEvaluatingReplicabilitySocial2018, opensciencecollaborationEstimatingReproducibilityPsychological2015} and among many possible explanations, one relates to a feature of study design: statistical power. In particular, it is plausible for original studies to have lower statistical power than their replications. In case of underpowered studies, we are usually aware of the lower probability of detecting an effect if this actually exists, but the less obvious consequences on effect size estimation are often neglected. When underpowered studies are analyzed using thresholds, such as statistical significance levels, effects passing such thresholds have to exaggerate the true effect size \parencite{buttonPowerFailureWhy2013, gelmanTypeErrorMight2017, ioannidisWhyMostDiscovered2008, ioannidisEmergenceLargeTreatment2013, laneEstimatingEffectSize1978}. Indeed, as will be extensively shown below, in underpowered studies only large effects correspond to values that can reject the null hypothesis and be statistically significant. As a consequence, if the original study was underpowered and found an exaggerated estimate of the effect, the replication effect will likely be smaller.

The concept of statistical power finds its natural development in the Neyman-Pearson framework of statistical inference and this is the framework that we adopt in this contribution. Contrary to the Null Hypothesis Significance Testing (NHST), the Neyman-Pearson approach requires to define both the \textit{Null Hypothesis} (i.e., usually, but not necessarily, the absence of an effect) and the \textit{Alternative Hypothesis} (i.e., the magnitude of the expected effect). Further discussion on the Neyman and Pearson approach and a comparison with the NHST is available in \textcite{altoeEnhancingStatisticalInference2020} and \textcite{gigerenzerNullRitualWhat2004}.
When conducting hypothesis testing, we usually consider two inferential risks:the Type I error (i.e., the probability $\alpha$ of rejecting the Null Hypothesis if this is true) and the Type II error (i.e., the probability $\beta$ of not rejecting the Null Hypothesis if this is false). Then, statistical power is defined as the probability 1-$\beta$ of finding a statistically significant result if the Alternative Hypothesis is true. All this leads to a narrow focus on statistical significance in hypothesis testing, overlooking another important aspect of statistical inference, namely, the effect size estimation.

When effect size estimation is conditioned on the statistical significance (i.e., effect estimates are evaluated only if their p-values are lower than $\alpha$), effect size exaggeration is a corollary consequence of low statistical power that might not be evident at first.This point can be highlighted considering the Type M (magnitude) and Type S (sign) errors characterizing a study design \parencite{gelmanPowerCalculationsAssessing2014}. Given a study design (i.e., sample size, statistical test directionality, $\alpha$ level and plausible effect size formalization), Type M error indicates the factor by which a statistically significant effect would be, on average, exaggerated. Type S error indicates the probability to find a statistically significant effect in the opposite direction to the one considered plausible. The analysis that researchers perform to evaluate the Type M and Type S errors in their research practice is called \emph{design analysis}, given the special focus posed into considering the design of a study \parencite{altoeEnhancingStatisticalInference2020, gelmanPowerCalculationsAssessing2014}.

Both errors are defined starting from a reasoned guess on the plausible magnitude and direction of the effect under study, which is called \emph{plausible effect size} \parencite{gelmanPowerCalculationsAssessing2014}. A plausible effect size is an assumption the researchers make about which is the expected effect in the population. This should not be based on some noisy results from a pilot study but, rather, it could derive from an extensive evaluation of the literature (e.g., theoretical or literature reviews and meta-analyses).  When considering the published literature to define the plausible effect size, however, it is important to take into account the presence of publication bias \parencite{francoPublicationBiasSocial2014} and consider techniques for adjusting for the possible inflation of effect size estimates \parencite{andersonSampleSizePlanningMore2017}. For example if, after taking into account possible inflations, all the main results in a given topic, considering a specific experimental design indicate that the correlation ranges between $r = .15$ and $r =.25$, we could reasonably choose as plausible effect size a value within this range. Or even better, we could consider multiple values to evaluate the results in different scenarios. Note that the definition of a plausible effect size is inevitably highly context dependent so any attempt to provide reference values would not be useful , instead it would prevent researchers from reasoning about the phenomenon of interest. Even in extreme cases where no previous information is available, which would question the exploratory/confirmatory nature of the study, researchers could still evaluate which effect would be considered relevant (e.g., from clinical or economic perspective) and define the plausible effect size according to that.

Why do these errors matter? The concepts of Type M and Type S errors allow enhancing researchers’ awareness on a complex process such as statistical inference. It gives a further tool that can be used to interpret and understand the important role of statistical power both when designing a new study or when evaluating previous results from the literature. In particular, it highlights the unwanted (and often overlooked) consequences on effect estimation when filtering for statistical significance in underpowered studies. The exaggeration of effect sizes, in the right or in the wrong direction, has important implications on a theoretical and applied level. On a theoretical level, studies’ designs with high Type M and Type S errors can foster distorted expectations on the effect under study, triggering a vicious cycle for the planning of future studies. This point is relevant also for the design of replication studies, which could turn out to be underpowered if they do not take into account possible inflations of the original effect \parencite{buttonPowerFailureWhy2013}. When studies are used to inform policymaking and real-world interventions, implications can go beyond the academic research community and can impact society at large. In these settings, we could assist to a “hype and disappointment cycle” \parencite{gelmanOverconfidenceResearchCertainty2019}, where true effects turn out to be much less impressive than expected. This can produce undesirable consequences on people’s lives, a consideration that invites researchers to assume responsibility in effectively communicating the risks related to effects quantification.

Type M (magnitude) and Type S (sign) errors are not widely known in the psychological research community but their consideration during the research process has the potential to improve current research practices, for example, by increasing the awareness that design choices have on possible studies' results. In a previous work we illustrated Type M and Type S errors using Cohens’\emph{d} as a measure of effect size \parencite{altoeEnhancingStatisticalInference2020}. The purpose of the present contribution is to further increase familiarity with Type M and Type S errors, considering another common effect size measures in psychology: Pearson correlation coefficient, $\rho$.  Weaim to provide an accessible introduction to the Design Analysis framework and enhance Type M and Type S errors understanding by means of several examples. The rest of this article is organized as follows: introduction to Type M and Type S errors; description of what is a design analysis and how to conduct one; analysis of Type S and Type M errors when varying alpha levels and hypothesis directionality. Moreover, the two appendices present further implications of design analysis for Pearson correlation (Appendix \ref{sec:appendix_a}) and an extensive illustration of the R functions for design analysis for Pearson correlation (Appendix \ref{sec:appendix_b}).

@@

Pearson correlation coefficient is a standardized effect size measure indicating the strength and the direction of the relationship between two continuous variables \parencite{cohenStatisticalPowerAnalysis1988, ellisEssentialGuideEffect2010}. Even though the correlation coefficient is widely known, we briefly go over its main features using an example. Imagine that we were interested to measure the relationship between anxiety and depression in a population and we plan a study with \emph{n} participants, where, for each participant, we measure the level of anxiety (i.e., variable X) and the level of depression (i.e., variable Y). At the end of the study we will have n pairs of values X and Y. The correlation coefficient helps us answer the questions: how strong is the linear relationship between anxiety and depression in this population? Is the relationship positive or negative? Correlation ranges from -1 to +1, indicating respectively two extreme scenarios of perfect negative relationship and perfect positive relationship\footnote{Correlation indicates a relationship between variables but does not imply causation. We do not discuss
this relevant aspect here but we refer the interested reader to \parencite{rohrerThinkingClearlyCorrelations2018}}. Since the correlation coefficient is a dimensionless number, it is a signal to noise ratio where the signal is given by the covariance between the two variables ($cov(x,y)$) and the noise is expressed by the product between the standard deviations of the two variables ($S_x  S_y$; see Formula\ref{eq:correlation}). Following the conventional standards, in this contribution we will use the symbol $\rho$ to indicate the correlation in the population and the symbol \emph{r} to indicate the value measured in a sample.
\begin{equation}
\label{eq:correlation}
r=\frac{cov(x,y)}{S_x\ S_y}.
\end{equation}

@@

Researchers can consider Type M and Type S errors in their practice by performing a \emph{design analysis} \parencite{altoeEnhancingStatisticalInference2020, gelmanPowerCalculationsAssessing2014}. Ideally, a design analysis should be performed when designing a study. In this phase it is specifically called \emph{prospective design analysis} and it can be used as a sample size planning strategy where statistical power is considered together with Type M and Type S errors. However, design analysis can also be beneficial to evaluate the inferential risks in studies that have already been conducted and where the study design is known. In these cases, Type M and Type S errors can support results interpretation by communicating the inferential risks in that research design. When design analysis happens at this later stage, it takes the name of \emph{retrospective design analysis}. Note that retrospective design analysis should not be confused with post-hoc power analysis. A retrospective design analysis defines the plausible effect size according to previous results in the literature or other information external to the study, whereas the post-hoc power analysis defines the plausible effect size based on the observed results in the study and it is a widely-deprecated practice \parencite{goodmanUsePredictedConfidence1994a, gelmanDonCalculatePosthoc2019a}.

In the following sections we illustrate how to perform prospective and retrospective design analysis using some examples. We developed two R functions\footnote{An R-package was subsequently developed and now is available on CRAN, PRDA: Conduct a Prospective or Retrospective Design Analysis \url{https://cran.r-project.org/web/packages/PRDA/index.html}.} to perform design analysis for Pearson correlation, which are available at the page \url{https://osf.io/9q5fr/}. The function to perform a prospective design analysis is \texttt{pro\_r()}. It requires as input the plausible effect size (\texttt{rho}), the statistical power (\texttt{power}), the directionality of the test (\texttt{alternative}) which can be set as: “\texttt{two.sided}”, “\texttt{less}” or “\texttt{greate}r” . Type I error rate (\texttt{sig\_level}) is set as default at 5\% and can be changed by the user. The \texttt{pro\_r()} function returns the necessary sample size to achieve the desired statistical power, Type M error rate, the Type S error probability, and the critical value(s) above which a statistically significant result can be found. The function to perform retrospective design analysis is \texttt{retro\_r()}. It requires as input the plausible effect size, the sample size used in the study, and the directionality of the test that was performed. Also in this case, Type I error rate is set as default at 5\% and can be changed by the user.  The function \texttt{retro\_r()} returns the Type M error rate, the Type S error probability, and the critical value(s)\footnote{\emph{Critical value} is the name usually employed in hypotheses testing within the Neyman-Pearson framework. In the research practice this is also known as the \emph{Minimal Statistically Detectable Effect} \parencite{cookAssessingMethodsSpecify2014, phillipsStatisticalSignificanceSediment2001}} . For further details regarding the R functions refer to Appendix~\ref{sec:appendix_b}.

@@

On a concluding note, we would like to clarify the relationship between publication bias and Type M and Type S errors. While the two are related, they operate at two different levels. Publication bias refers to a publication system that favors statistically significant results over non-statistically significant findings. This phenomenon alone cannot explain the presence of exaggerated effects. Imagine if all studies in the literature were conducted with high statistical power, then statistically significant findings would probably not be so extreme. The problem of exaggerated effect sizes in the literature can be explained only by a combination of publication bias with studies that have low statistical power. As previously shown, statistical power and Type M and Type S errors are related to each other: low statistical power corresponds to higher Type M and Type S errors. In the same way as statistical power is a characteristic of a study design, so are Type M and Type S, however the two are qualitatively different in terms of the kind of reasoning they favor.
Statistical power is defined in terms of probability of rejecting the Null hypothesis and, even though this is based on an effect size of interest, the relationship “low power - high possibility of exaggeration” may not be straightforward for everyone. Instead, Type M and Type S errors directly quantify the possible exaggeration. Furthermore their consideration protects against another possible pitfall. It is quite widespread the knowledge that even the smallest effects can become statistically significant if the sample size is large enough. However, if a statistically significant result is found paired with a large effect size, the results may be considered robust. However, this is not true in all cases. Here, the missing piece of information is  statistical power. If power is considered, researchers would realize that a large effect was found in a context where there was a low probability to find it. What is the meaning? This interpretation is not explicitly stating an important consequence: the study may find effects that are overestimated, if statistically significant. On the contrary, this becomes immediately clear once Type M and Type S errors are considered retrospectively. In a similar fashion, considering Type M and Type S prospectively favors reason in terms of effect size rather than probability of rejecting the null when setting the sample size in a design analysis.

@@

However, in the case of $\rho \neq 0$, the sample correlation is no longer normally distributed. As we have previously seen, the sampling distribution is skewed for large values of $\rho$ and small sample sizes. Thus, the test statistic of interest does not follow a \emph{t}-distribution.\footnote{Note that the \emph{t}-distribution is defined as the distribution of a random variable T where $T = \frac{Z}{\sqrt{V/df}}$. With \emph{Z} a standard Normal, \emph{V} a Chi-squared distribution with \emph{df} the degrees of freedom. Thus, if the sample correlation is no longer approximately normally distributed the test-statistic is no longer \emph{t}-distributed.} To overcome this issue, the Fisher transformation was introduced \parencite{fisherFrequencyDistributionValues1915}:
\begin{equation}
  F(r) = \frac{1}{2}\ ln \frac{1+r}{1-r} = \text{arctanh}(r).
\end{equation}
Applying this transformation, the resulting sampling distribution is approximately Normal with $\text{mean} = F(\rho)$ and $\text{SE} = \frac{1}{\sqrt{n-3}}$. Thus, the test statistic follows a standard Normal distribution and statistical inference is performed considering the \emph{Z}-scores.
